---
title: "project1-api-dataset"
author: "Lin"
format: html
---

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(httr)
library(countrycode)
library(glue)
```

### Setup

We load our democracy data and filter to 2000 onward to avoid issues with historical countries like the Soviet Union that no longer exist and won't have GDP data.

```{r}
#| message: false
democracy_data <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2024/2024-11-05/democracy_data.csv')

democracy_recent <- democracy_data |>
  filter(year >= 2000)
```

### Intro

We use the API-Ninjas GDP endpoint to get historical GDP data for each country. The API returns year-by-year GDP statistics including GDP per capita and GDP growth rate. We iterate over all unique countries using map().

### API Key

```{r}
#| eval: false

my_key <- ""
```

### API Function

takes a 3-letter country code and returns a GDP data frame for that country.

```{r}
#| eval: false
get_gdp <- function(country, key = my_key) {
  
  Sys.sleep(1)
  
  url <- glue("https://api.api-ninjas.com/v1/gdp?country={country}&X-Api-Key={key}")
  my_data <- safely(fromJSON)(url)
  
  if (is.null(my_data$result)) {
    return(NULL)
  } else {
    return(my_data$result)
  }
}

```

### Iterating all the countries from API data set

```{r}
#| eval: false

codes <- democracy_recent |>
  distinct(country_code) |>
  pull(country_code)

gdp_list <- map(codes, get_gdp)

gdp_df <- gdp_list |>
  compact() |>
  bind_rows()

write_csv(gdp_df, "/Users/roland/Stat 431/lab-1/gdp_data.csv")
```

### Combining to the original data set

```{r}

combined <- democracy_recent |>
  left_join(gdp_df, by = c("country_code" = "country", "year"))

```

